SMT-Boosted Security Types for Low-Level MPC

### 2025-11-24 toplas26/sty.tex
checkpoint

To proceed, we define a well-formedness property of tuples $\prog,\Gamma,R$

@@

Property (i) ensures that views do not reveal information about secrets.
Property (ii) ensures the key property of sharing-- that individual shares

@@

With the definition of ${OK}$ in place, we can define what we mean by soundness
of $\genshares$. In this definition, the first condition establishes that
initial shares are independent of honest secrets, and the second establishes
that they reveal no more than their reconstruction. These conditions are
obviously met by ``vanilla'' additive or Shamir shares which generate
shares in uniform marginal distributions.

\begin{definition}
  \label{def-genshares}
  We say that $\genshares$ is \emph{sound} iff given any $\prog$ with
  $\vars(\prog) = S \cup V \cup O \cup R$
  and $\phi$ and $\rx{w}{\cid} \not \in R$ and $\genshares(\phi,\rx{w}{\cid}) =
  \phi_1,\phi_2$ we have for all $a \in \setit{1,2}$:
  $$
  \sep{\progd(\prog)}{(S \cup V \cup O \cup \setit{\phi})}{\setit{\phi_a}}
  $$
\end{definition}

@@

Next, we show that interactive typing rules preserve well-formedness of type
environments. This Lemma follows by Lemma \ref{lemma-sty-noninteractive-sound},
and the security of share generation using OTPs as articulated in
Definition \ref{def-genshares}-- that is, shares
generated by $\genshares$ are in uniform marginal distributions. 
\begin{lemma}
  \label{lemma-OK}
  Given $\prog,\Gamma_1,R_1  : {OK}$
  and $\toeq{\prog}  \vdash \Gamma_1, R_1 \stredx \Gamma_2, R_2$.
  Then $\toeq{\prog}, \Gamma_2, R_2 : {OK}$.
\end{lemma}
\begin{proof}
  The proof follows by case analysis on  $\toeq{\prog}  \vdash \Gamma_1, R_1 \stredx \Gamma_2, R_2$.
  In case \TirName{GenShares} the result follows by Definition \ref{def-genshares},
  which satisfies relevant conditions (i-ii,iv) of Definition \ref{def-OK}. In case
  \TirName{SecOpen} the public value must be reconstructed shares so Lemma
  \ref{lemma-sty-noninteractive-sound} relevant conditions (i-ii), and the
  the requirement that the public value be masked with an OTP satisfies conditions
  (iii) and (iv) of Definition \ref{def-OK}. In case \TirName{Reveal} since
  the output value must be reconstructed shares, Lemma \ref{lemma-sty-noninteractive-sound}
  satisfies relevant case (ii) of  Definition \ref{def-OK}. 
\end{proof}

>>>>

Now we define what we mean by soundness of $\genshares$. In essence
we mean perfect secrecy \cite{barthe2019probabilistic} in the context
of protocols where multiple encodings can occur. These
conditions are obviously met by, e.g., ``vanilla'' additive or Shamir
shares which generate shares in uniform marginal distributions.
\begin{definition}
  \label{def-genshares}
  We say that $\genshares$ is \emph{sound} iff given any $\prog$ with
  $\vars(\prog) = S \cup V \cup O \cup R$
  and $\phi$ and $\rx{w}{\cid} \not \in R$ and $\genshares(\phi,\rx{w}{\cid}) =
  \phi_1,\phi_2$ we have for all $a \in \setit{1,2}$:
  $$
  \sep{\progd(\prog)}{(S \cup V \cup O \cup \setit{\phi})}{\setit{\phi_a}}
  $$
\end{definition}

Next we define a well-formedness property of tuples $\prog,\Gamma,R$

@@

This is a representation invariant that we will show is preserved by
typing, and under closure conditions (Definition \ref{def-sty-closed})
guarantees confidentiality (Theorem \ref{theorem-OK})$.
Property (i) ensures that views do not reveal information about secrets
consistent with noninterference modulo output.
Property (ii) ensures a key property of sharing-- that individual shares

@@

@@

Next, we show that interactive typing rules preserve well-formedness of type
environments. This Lemma follows by Lemma \ref{lemma-sty-noninteractive-sound},
and the security of share generation using OTPs as articulated in
Definition \ref{def-genshares}-- that is, shares
generated by $\genshares$ are in uniform marginal distributions. 
\begin{lemma}
  \label{lemma-OK}
  Given $\prog,\Gamma_1,R_1  : {OK}$
  and $\toeq{\prog}  \vdash \Gamma_1, R_1 \stredx \Gamma_2, R_2$.
  Then $\toeq{\prog}, \Gamma_2, R_2 : {OK}$.
\end{lemma}
\begin{proof}
  The proof follows by case analysis on  $\toeq{\prog}  \vdash \Gamma_1, R_1 \stredx \Gamma_2, R_2$.
  In case \TirName{GenShares} the result follows by Definition \ref{def-genshares},
  which satisfies relevant conditions (i-ii,iv) of Definition \ref{def-OK}. In case
  \TirName{SecOpen} the public value must be reconstructed shares, so Lemma
  \ref{lemma-sty-noninteractive-sound} enforces relevant conditions (i-ii) of Definition
  \ref{def-OK}, and the requirement that the public value be masked with an OTP satisfies conditions
  (iii) and (iv) of Definition \ref{def-OK}. In case \TirName{Reveal} since
  the output value must be reconstructed shares, Lemma \ref{lemma-sty-noninteractive-sound}
  satisfies relevant case (ii) of  Definition \ref{def-OK}. 
\end{proof}
